|

### 2023-05-31 manuscript/Chapter2-appendix3.Rmd
update appendix 3 with fig s2

```{r figS2, out.width = "80%", fig.cap = "**Figure S2.** Posterior median differences in the correlations of players when they were advanced vs novice along with their 95% HPD intervals. The difference is displayed on the x axis and the parameter correlations are displayed on the y axis. Positive values indicate that the correlation was greater when predators where advanced, while negative values indicate that the correlation was greater when predators where novices. The results are from the MDHGLM that includes the outlier."}

>>>>

```{r figS2, out.width = "100%", fig.cap = "**Figure S2.** Posterior median differences in the correlations of players when they were advanced vs novice along with their 95% HPD intervals. The difference is displayed on the y axis and the parameter correlations are displayed on the x axis. Positive values indicate that the correlation was greater when predators where advanced, while negative values indicate that the correlation was greater when predators where novices. The results are from the MDHGLM that includes the outlier."}
